---
title: "Simple document"
author: "You Wu"
date: "2023-09-12"
output: github_document
---

```{r,echo=FALSE,message=FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2
This code is borrowed from last lecture; it creates a dataframe for plotting.
```{r}

plot_df=
  tibble(
    x=rnorm(1000,sd=0.5),
    y=1+2*x+rnorm(1000)
  )
```
Next up i a histogram of the `x` variable in `plot_df`
```{r}
ggplot(plot_df,aes(x=x))+geom_histogram()
```

Lastly, I'll do a scatterplot.

```{r}
ggplot(plot_df,aes(x=x,y=y))+geom_point()
```

# Section 3: Learning assesment!

The chunk below creates a dataframe containing a sample of size 500 from a 
random normal variable with mean equals to 1, constructs the specified logical vector, takes the 
absolute value of each element of that sample,and produces a histogram of 
the absolute value. The code chunk also finds the median of the sample and
stores it for easy in-line printing.
```{r}
la_df=
  tibble(
    num_samp=rnorm(500,mean=1),
    log_vecc=num_samp>0,
    abs_val=abs(num_samp)
  )
ggplot(la_df,aes(x=abs_val))+geom_histogram()
```

# Section 4:

I can take the mean of the sample, too!
The mean is `r round(mean(samp),digits=4)`.